Capturing the shape of our experiences and how we remember them

### 2018-08-16 paper/main.tex
moved figures to supp

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
% \usepackage{amsmath}
% \newcommand{\rpm}{\raisebox{.2ex}{$\scriptstyle\pm$}}
% \DeclareMathOperator*{\argmax}{arg\,max}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=\textwidth]{figs/2_eventseg.pdf}
\caption{\small \textbf{Modelling naturalistic stimuli and recall.} A depiction of our analysis pipeline. For all plots, darker colors indicate greater values and the range of each plot is 0-1.  A). A timepoints (1976) by topics (100) matrix representing the video stimulus.  Each row represents the most likely mixture of topics for a given timepoint (i.e. topic weights). Each column represents a different topic. B). A timepoints (1976) by topics (100) matrix representing participant \#13's recall. C). A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model. The white boxes represent `events' recovered by a hidden Markov model. D). A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13. E). An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.  F). An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model. G. A recall events (27) by video events (34) correlation matrix for participant \#13. The cells with a yellow border identify the video event with the highest correlation to a given recall event. F. A group averaged recall events (34) by video events (34) correlation matrix.  The cells with yellow borders are the video event with the highest correlation to a given average recall event.}
\label{fig:model}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/3_list_learning.pdf}
\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A). The probability of first recall as a function of the serial position of the event during encoding. B). A lag-conditional response probability curve. Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag. C). Proportion of events recalled as a function of serial position. All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
\label{fig:list-learning}
\end{figure}

@@

@@

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/supp1_corrmats.pdf}
\caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.  The yellow boxes represent ``events'' identified by a hidden Markov model.}
\label{fig:corrmats}
\end{figure}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
% \usepackage{amsmath}
% \newcommand{\rpm}{\raisebox{.2ex}{$\scriptstyle\pm$}}
% \DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{newfloat}
\DeclareFloatingEnvironment[name={Supplementary Figure},fileext=lof]{suppfigure}

@@

@@

To conclude, let's revisit the question of what it means to remember something. We assert that episodic memories are not veridical snapshots from the past, and so we should stop treating (and modelling) them as such.  Rather, episodic memories are better described as echoes of a prior experience that are shaped by other past experiences as well as the current context. Furthermore

@@

\begin{suppfigure}[ht!]
\centering
\includegraphics[width=\textwidth]{figs/supp1_eventseg.pdf}
\caption{\small \textbf{Modelling naturalistic stimuli and recall.} A depiction of our analysis pipeline. For all plots, darker colors indicate greater values and the range of each plot is 0-1.  A). A timepoints (1976) by topics (100) matrix representing the video stimulus.  Each row represents the most likely mixture of topics for a given timepoint (i.e. topic weights). Each column represents a different topic. B). A timepoints (1976) by topics (100) matrix representing participant \#13's recall. C). A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model. The white boxes represent `events' recovered by a hidden Markov model. D). A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13. E). An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.  F). An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model. G. A recall events (27) by video events (34) correlation matrix for participant \#13. The cells with a yellow border identify the video event with the highest correlation to a given recall event. F. A group averaged recall events (34) by video events (34) correlation matrix.  The cells with yellow borders are the video event with the highest correlation to a given average recall event.}
\label{fig:model}
\end{suppfigure}

\begin{suppfigure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/supp2_corrmats.pdf}
\caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.  The yellow boxes represent ``events'' identified by a hidden Markov model.}
\label{fig:corrmats}
\end{suppfigure}

\begin{suppfigure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/supp3_list_learning.pdf}
\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A). The probability of first recall as a function of the serial position of the event during encoding. B). A lag-conditional response probability curve. Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag. C). Proportion of events recalled as a function of serial position. All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
\label{fig:list-learning}
\end{suppfigure}
